Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
add gwenole as author #26
@GwennoleChappron could you provide your orcid ID ?

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
\authorrunning{V. Chabannes et al.}

>>>>

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{Luca Berti\inst{1} \and 
Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Gwennolé Chappron \inst{1}\orcidID{0000-0002-0001-0002} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
\authorrunning{V. Chabannes et al.}
